Results

### 2022-01-24 Manuscript/Manuscript_Discussion.Rmd
small corrections

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the queried databases in terms of traffic and download quota.
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].\

For the framework's record classification module we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies, bringing further improvements at various levels.\
The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
This approach allows also to find term connections across fields, for example a term having a different relevancy if associated with a specific author.
The same technique but with different parameters was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\

The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
However, its Bayesian foundation provides further benefits:
less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which showed performance stabilisation during the hyperparameter evaluation.\
We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it was demonstrated to be slightly detrimental (Supplemental Material S2) compared to simple ensembling.\

@@

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

@@

The last module of our framework is a data-driven query generation algorithm.
Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query builder.
The aim is to generate a second query that helps find records missed during the first session search.
The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\

As reported, our framework builds on modularity.
We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and uncertainty zone.
However, each of its components could benefit considerably from the recent improvements in text mining.\
For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
Word embedding could be worth exploring:
this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.

>>>>

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the two more (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found only in one of the different data sources, and no positive record was present in all of them (data not shown).\
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of online citation databases in terms of traffic and download quotas.
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allows to increase the positivity rate in the initial training set [@wallace2010active].\

For the framework's record classification module, we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies but also bringing further improvements at various levels.\
The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
This approach allows also to find term connections across fields, for example a term having a different relevancy if associated with a specific author.
The same technique but with different parameters was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\

The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
However, its Bayesian foundation provides further benefits:
less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilised during the hyperparameter evaluation.\
We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2) compared to simple ensembling.\

@@

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

@@

The last module of our framework is a data-driven query generation algorithm.
Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
The aim is to generate a second query that helps find records missed during the first session search.
The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\

As reported, our framework builds on modularity.
We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and the exploit of the derived uncertainty in predictions.
However, each of its components could benefit considerably from the recent improvements in text mining.\
For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
Word embedding could be instead worth exploring:
this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.

### 2022-01-24 Manuscript/Manuscript_Results.Rmd
small edits to Results table
small corrections

The labeled records were used to train the Bayesian classification model used to label the remaining records. After seven classification and review (CR) iterations (three resulting in new positive matches and four extra replications to account for stochastic variability), a total of `r num_last_positives` positives matches were found, requiring manual review of `r tot_reviewed` records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
It is possible to observe how the number of records that required manual review dropped rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
This phenomenon is better depicted in Fig. 1 of the Supplemental Material S2, showing the mixture distribution of the PPDs of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked (they concentrate in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.

`r print_table(annotation_results, caption = "**Table 2**. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.", label = "Table 2")`

@@

The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
Some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the EMBASE, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE;
compared with the first session, the relative weight of EMBASE and Pubmed was decreased, while the amount of content specificity was greatly increased, as it was for SCOPUS.
After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
Once joined with the session 1 records and duplicates removed, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.

`r english::as.english(n_review_rounds) %>% str_to_title()` CR rounds were necessary to complete the second session classification, with just `r sum(session_summary[-1, 'Unlab. -> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
The first CR iteration required the user to review a substantial number of records (1,273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework hyperparameter tuning) was sufficient to drop this number to just 190 in the subsequent round.
An evaluation of the convergence (Figure 1, Supplemental Material S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set generated during Session 1.
This behaviour can be useful to spot classification errors and inconsistencies.
Considering both sessions, `r tot_reviewed` records were reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) were found.

Again, the evaluation of the inclusion rate of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic
A subsample of the terms is reported in Table 2 of Supplemental Material S2.

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 completely manually labelled records.
The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
The results of the hyperparameter tuning are reported in Table 3 of Supplemental Material S2.
Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that most impact performance.

@@

# Creating these summary is quite demanding, so it's better to cache them
# explicitly
perf_file <- file.path('Manuscript', 'Performance_summary.rds')

@@

To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for details).
The surrogate model show the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\

Figure 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool;
some relevant record was found even close to the end of the heuristically ordered list of records.\

Table 3 shows various performance indexes for both sessions, both descriptive (Total records, Reviewed records, Observed positive matches) and estimated through the surrogate model (Expected efficiency, Predicted positive matches, Expected sensitivity, $R^2$).\
In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.\

`r print_table(perf_table, caption = '**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals', allow_math = TRUE, label = "Table 3")`

```{r performance plot, cache = FALSE, fig.width=6, fig.height=2.5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

>>>>

The labeled records were used to train the Bayesian classification model used to label the remaining records. After seven classification and review (CR) iterations (three resulting in new positive matches and four extra replications to account for stochastic variability), a total of `r num_last_positives` positives matches were found, requiring manual review of `r tot_reviewed` records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
It is possible to observe how the number of records that required manual review dropped rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
This phenomenon is better depicted in Fig. 1 of the Supplemental Material S2, showing the mixture distribution of the PPDs of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked (ie., gets concentrated in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.

`r print_table(annotation_results, caption = "**Table 2**. Results of the automatic classification and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.", label = "Table 2")`

@@

The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
The engine was able to pick up the central concept of the research topic, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of pathogen spreading over hospital networks.
Some terms were considered highly relevant by the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by using advanced, non-linear machine learning.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the EMBASE, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE;
compared with the first session, the relative weight of EMBASE and Pubmed was decreased, while the amount of content specificity was greatly increased, as it was for SCOPUS.
After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
Once joined with the session 1 records and removal of duplicates, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.

`r english::as.english(n_review_rounds) %>% str_to_title()` CR rounds were necessary to complete the second session classification, with just `r sum(session_summary[-1, 'Unlab. -> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
The first CR iteration required the user to review a substantial number of records (1,273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework hyperparameter tuning) was sufficient to drop this number to just 190 in the subsequent round.
An evaluation of the convergence (Figure 1, Supplemental Material S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set generated during Session 1.
This behaviour can be useful to spot classification errors and inconsistencies.
Considering both sessions, `r tot_reviewed` records were manually reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) confirmed positive matches were found.

Again, the evaluation of the inclusion rate of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic
A subsample of the relevant terms used by the model in the second session is reported in Table 2 of Supplemental Material S2.

@@

As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 manually labelled records.
The analysis suggested the following combination of parameters as the best performing: an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
This combination of parameters was associated with a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
The detailed results of the hyperparameter tuning ananlysis are reported in Table 3 of Supplemental Material S2.
Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mostly impacted performance.

@@

# Creating these summaries is quite demanding, so it's better to cache them
# explicitly
perf_file <- file.path('Manuscript', 'Performance_summary.rds')

@@

To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for the details).
The surrogate model showed the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\

Figure 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool,
with some positive matches found close to the end of the heuristically ordered list of records.\

Table 3 shows various performance indexes for both sessions, both descriptive (Total records, Reviewed records, Observed positive matches) and estimated through the surrogate model (Expected efficiency, Predicted positive matches, Expected sensitivity, $R^2$).\
In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
In session 2 we observed a drop in the expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability of being a positive match can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.\

`r print_table(perf_table, caption = '**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals.', allow_math = TRUE, label = "Table 3")`

```{r performance plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}
